### 2020-12-12 exploratory/2020-11/plots.Rmd
Use set union method

debug_dat %>% filter(seed ==1, ref_weight == 'distance', dataset == 'human') %>% pull(is_correct)
debug_dat %>% filter(seed ==2, ref_weight == 'distance', dataset == 'human') %>% pull(is_correct)

>>>>

debug_dat %>% filter(seed ==1, ref_weight == 'simple', dataset == 'human') %>% pull(is_correct)
debug_dat %>% filter(seed ==2, ref_weight == 'simple', dataset == 'human') %>% pull(is_correct)
